Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-25 src/tex/ms.tex
update with macros etc

@@

\usepackage{showyourwork}
\usepackage[perpage]{footmisc}
\usepackage{colortbl}
\usepackage{lineno}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{appendix}
\definecolor{Gray}{gray}{0.9}
\linenumbers

@@

@@

\begin{abstract}
We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
binary black hole masses and spins using the 69 confident observations in GWTC-3. We find the same features previously recovered 
with similarly flexible models in the mass distribution, namely the peaks in merger rates at \~10\msun and \~35\msun. 
We apply our method to investigate whether the spin components are indendendenty distributed with a model agnositc way, where we find that 
the spin magnitude distribution seems to be quite consistently IID, with XX\% of black hole spins below XX at XX\% credibility. We report 
slight evidence of tilt distributions that do not peak at $\cos(\theta_i) = 1$ as previous models assumed, and slight evidence that 
the components are distributed differently, in contrast to the spin magnitude distribution. While we do not find signs of a significant
zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
the non-singular Beta distribution and \textsc{Default} model assumes. 
\end{abstract}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful and discussions during the preparation this manuscript, 
along with helpful comments on an early draft by Tom Callister.
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{jax},
\textsc{numpyro},
\bruce{CITE ALL ABOVE}
}
\bibliography{bib}{}
\bibliographystyle{aasjournal}

>>>>

\newcommand{\CIPlusMinus}[1]{{#1[median]^{+#1[error plus]}_{-#1[error minus]}}}
\newcommand{\CIBoundsBracket}[1]{{[#1[5th percentile], #1[95th percentile]]}}
\newcommand{\CIBoundsDash}[1]{{#1[5th percentile]\textendash#1[95th percentile]}}

@@

\usepackage{showyourwork}
\usepackage[perpage]{footmisc}
\usepackage{colortbl}
\usepackage{lineno}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{appendix}
\input{macros}

\definecolor{Gray}{gray}{0.9}
\linenumbers

@@

\author{Jaxen Godfrey}
\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}

\author{Alexis Vives}
\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}

@@

\begin{abstract}
We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
binary black hole masses and spins using the 69 confident observations in GWTC-3. We find the same features previously recovered 
with similarly flexible models in the mass distribution, namely the peaks in merger rates at \~10\msun and \~35\msun. 
We apply our method to investigate whether the spin components are indendendenty distributed with a model agnositc way, where we find that 
the spin magnitude distribution seems to be quite consistently IID, with XX\% of black hole spins below XX at XX\% credibility. We report 
slight evidence of tilt distributions that do not peak at $\cos(\theta_i) = 1$ as previous models assumed, and slight evidence that 
the components are distributed differently, in contrast to the spin magnitude distribution. While we do not find signs of a significant
zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
the non-singular Beta distribution and \textsc{Default} model assumes. \result{$\CIPlusMinus{\macros[MSPlineIIDCompSpins][peakCosTilt]}$}
\result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt1]}$}, \result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt2]}$}
\end{abstract}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful discussions during the preparation this manuscript, 
along with helpful comments on an early draft by Tom Callister.
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{jax},
\textsc{numpyro},
\bruce{CITE ALL ABOVE}
}
\bibliography{bib}{}
\bibliographystyle{aasjournal}
